An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data

### 2015-03-24 paper/paper7/paper7-evaluation.tex
evaluation

@@

@@

\begin{itemize}
	\item DwB Resource Discovery Portal
	\begin{itemize}
	  \item Metadata records for each study are available on the study landing pages.
		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \url{http://270a.info/} (see the VoID which points to other
VoIDs) is full of data sets (probably close to 10k) using RDF Data Cube,
and some of those also include XKOS.
\end{itemize}

>>>>

% tables
\usepackage{array,graphicx}
\usepackage{booktabs}
\usepackage{pifont}
\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK{\ding{51}}
\usepackage{booktabs}
\newcommand*\ON[0]{$\surd$}

\usepackage{tablefootnote}

\usepackage{float}

@@

\section{Evaluation}

\subsection{Legend}

\begin{table}
	\centering
		\begin{tabular}{c|l}
      \textbf{Symbol} & \textbf{Description} \\		
			\emph{X} & \textbf{Validation Successful} \\
			\hline
			\textbf{\textgreater} \emph{X} & \textbf{Poor Performance/Scaling} \\
			\hline
      \ding{55} & \textbf{Very Poor Performance/Scaling} \\
			\hline
			$\dagger$ & \textbf{SPARQL Endpoint Error}
		\end{tabular}
	\caption{Legend}
	\label{tab:legend}
\end{table}

\textbf{Validation Successful:} 
\emph{X} indicates the number of raised constraint violation triples.

\textbf{Poor Performance/Scaling:}
The performance of the implementation of the underlying SPARQL CONSTRUCT query 
is too poor to get all resulting constraint violation triples. 
Therefore, a limit of \emph{X} result constraint violation triples is set. 
It is likely that there are more than \emph{X} constraint violations.
Although, the result set contains not the whole set of raised constraint violation triples,
the constraint can be used as an indicator if there data not conforming to the constraint and
to resolve constraint violations step by step. 
As part of future work, the performance will be improved.

\textbf{Very Poor Performance/Scaling:} 
The performance of the implementation of the underlying SPARQL CONSTRUCT query 
is too poor to get any results, even though a limit of result constraint violation triples is set. 
As part of future work, the performance will be improved.

@@

\begin{itemize}
	\item DwB Discovery Portal
	\begin{itemize}
	  \item Metadata records for each study are available on the study landing pages.
		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
	\end{itemize}
\end{itemize}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Disco Data Sets} \\		
      \hline
    Missy & Microdata Information System\tablefootnote{\url{http://www.gesis.org/missy/eu/missy-home}} \\
		DwB & DwB Discovery Portal\tablefootnote{\url{http://dwb-dev.nsd.uib.no/portal}} \\
		DDA-SND & DDA and SND DDI-RDF\tablefootnote{\url{http://ddi-rdf.borsna.se/}} \\ 
		\end{tabular}
	\caption{Disco Data Sets Abbreviations}
	\label{tab:disco-data-sets-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{9}{c}{\textbf{Counts}}
    \\  \cmidrule{2-10}
    \\       \textbf{Data Sets}
           & \textbf{\rot{triples}}
           & \textbf{\rot{disco:StudyGroup}}
           & \textbf{\rot{disco:Study}}
           & \textbf{\rot{disco:LogicalDataSet}}
           & \textbf{\rot{disco:Universe}}
					 & \textbf{\rot{disco:Variable}}
					 & \textbf{\rot{disco:Question}}
				   & \textbf{\rot{disco:SummaryStatistics}}
					 & \textbf{\rot{disco:CategoryStatistics}}
					 & \textbf{\rot{skos:Concept}}
    \\ \midrule
    Missy &  &  &  &  &  & \\
		DwB & 2,332,802 & 0 & 1,387 & 1,367 & 2,796 & 446,806 & 0 & 0 & 0 & 0 \\
		DDA-SND & 2,271,415 & 0 & 1,490 & 0 & 10,188 & 80,070 & 139,237 & 0 & 0 & 290,963 \\ 
    \bottomrule
    \end{tabular}
    \caption{Disco Data Sets Overview}
		\label{tab:disco-overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
      \hline
      Missy & \textcolor{red}{XXXXX} \\
			DwB & \url{http://dwb-dev.nsd.uib.no/sparql} \\
			DDA-SND & \url{http://ddi-rdf.borsna.se/endpoint/} \\
		\end{tabular}
	\caption{Disco SPARQL Endpoints}
	\label{tab:disco-sparql-endpoints}
\end{table}

@@

\begin{itemize}
  \item overview over Data Cube data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}} 
  \item \url{http://ontologycentral.com/}
\end{itemize}

%\begin{table}
	%\centering
		%\begin{tabular}{l|c|c|c|c|c|c}
      %\textbf{Data Set} & \textbf{triples} & \textbf{data sets} & \textbf{data structure definitions} & \textbf{observations} & \textbf{slices} & \textbf{dimensions} \\		
      %\hline
      %European Central Bank (ECB)\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} &  &  &  &  &  &  \\
			%UNESCO Institute for Statistics (UIS)\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} &  &  &  &  &  &  \\
			%International Monetary Fund (IMF)\tablefootnote{\url{http://www.imf.org/external/index.htm}} &  &  &  &  &  &  \\
			%Bundesamt für Statistik - Swiss Federal Statistics (BFS)\tablefootnote{\url{http://www.bfs.admin.ch/}} &  &  &  &  &  &  \\
			%Food and Agriculture Organization of the United Nations (FAO)\tablefootnote{\url{http://www.fao.org/home/en/}} &  &  &  &  &  &  \\
			%World Bank (WB)\tablefootnote{\url{http://www.worldbank.org/}} &  &  &  &  &  &  \\
			%Federal Reserve Board (FRB)\tablefootnote{\url{http://www.federalreserve.gov/}} &  &  &  &  &  &  \\
			%Transparency International (TI)\tablefootnote{\url{http://www.transparency.org/}} &  &  &  &  &  &  \\
			%Organisation for Economic Co-operation and Development (OECD)\tablefootnote{\url{http://www.oecd.org/}} &  &  &  &  &  &  \\
			%Bank for International Settlements (BIS)\tablefootnote{\url{http://www.bis.org/}} &  &  &  &  &  &  \\
			%Australian Bureau of Statistics (ABS)\tablefootnote{\url{http://abs.gov.au/}} &  &  &  &  &  &  \\
		%\end{tabular}
	%\caption{Data Cube Data Sets}
	%\label{tab:data-cube-data-sets}
%\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Data Cube Data Sets} \\		
      \hline
    ECB & European Central Bank\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
		UIS & UNESCO Institute for Statistics\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} \\
		IMF & International Monetary Fund\tablefootnote{\url{http://www.imf.org/external/index.htm}} \\
		BFS & Bundesamt für Statistik - Swiss Federal Statistics\tablefootnote{\url{http://www.bfs.admin.ch/}} \\
		FAO & Food and Agriculture Organization of the United Nations\tablefootnote{\url{http://www.fao.org/home/en/}} \\
		WB & World Bank\tablefootnote{\url{http://www.worldbank.org/}} \\
		FRB & Federal Reserve Board\tablefootnote{\url{http://www.federalreserve.gov/}} \\
		TI & Transparency International\tablefootnote{\url{http://www.transparency.org/}} \\
		OECD & Organisation for Economic Co-operation and Development\tablefootnote{\url{http://www.oecd.org/}} \\
		BIS & Bank for International Settlements\tablefootnote{\url{http://www.bis.org/}} \\
		ABS & Australian Bureau of Statistics\tablefootnote{\url{http://abs.gov.au/}} \\
		IEEE-VIS & IEEE VIS Source Data \\
		ACORN-SAT & Australian Climate Observations Reference Network - Surface Air Temperature Dataset \\
		HDP & HealthData.gov Platform (HDP) on the Semantic Web \\
		Eurostat & The Eurostat Linked Data  \\
		Asturias & Nomenclator Asturias \\
		ISTAT & ISTAT Immigration (LinkedOpenData.it) \\
		ICANE & Statistical Office of Cantabria (Instituto Cántabro de Estadística, ICANE) \\
		EE-2009 & European Election Results 2009 \\
		EU-B & Standard Eurobarometer \\
		ECB-S & European Central Bank Statistics (PublicData.eu) \\
		CPV-2008 & Common Procurement Vocabulary (CPV) 2008 \\
		CPV-2003 & Common Procurement Vocabulary (CPV) 2003 \\
		GHI-2011 & Global Hunger Index (GHI) 2011 \\
		\end{tabular}
	\caption{Data Cube Data Sets Abbreviations}
	\label{tab:data-cube-data-sets-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{5}{c}{\textbf{Counts}}
    \\  \cmidrule{2-6}
    \\       \textbf{Data Sets}
           & \textbf{\rot{triples}}
           & \textbf{\rot{qb:DataSet}}
           & \textbf{\rot{qb:DataStructureDefinition}}
           & \textbf{\rot{qb:Observation}}
           & \textbf{\rot{qb:Slice}}
    \\ \midrule
    ECB & 468,899,474 & 55 & 46 & $>$11,000,000 & 428,698 \\
		UIS & 10,400,534 & 5 & 5 & 1,437,651 & 0 &  \\
		IMF & 35,688,446 & 4 & 8 & 3,603,719 & 0 &  \\
		BFS & 1,533,743 & 0 & 0 & 8 & 0 &  \\
		FAO & 53,000,000 & 10 & 10 & $>$7,100,000 & 0 \\
		WB & 174,006,552 & 9,466 & 59 & $>$17,000,000 & 0 \\
		FRB & 185,266,900 & 49 & 98 & $>$9,500,000 & 0 \\
		TI & 52,233 & 6 & 6 & 3,928 & 0 \\
		OECD & 304,995,160 & 136 & 140 & $>$12,000,000 & 0 \\
		BIS & 54,197,482 & 6 & 12 & 3,606,466 & 47,914 \\
		ABS & 2,357,400,000 & 253 & 257 & $>$11,000,000 & 0  \\
		IEEE-VIS & 19,935,340 & 0 & 0 & 1,350 & 0 \\
		ACORN-SAT & 61,406,503 &  &  &  &  &  \\
		HDP & 1,934,046,908 &  &  &  &  &  \\
		Eurostat & 8,000,000,000 &  &  &  &  &  \\
		Asturias & 4,508,050 &  &  &  &  &  \\
		ISTAT & 3,024,396 &  &  &  &  &  \\
		ICANE & 52,412 &  &  &  &  &  \\
		EE-2009 & 3,165 &  &  &  &  &  \\
		EU-B & 1,193,494 &  &  &  &  &  \\
		ECB-S & 10,000,000 &  &  &  &  &  \\
		CPV-2008 & 803,311 &  &  &  &  &  \\
		CPV-2003 & 546,135 &  &  &  &  &  \\
		GHI-2011 & 19,369 (dump) &  &  &  &  &  \\
    \bottomrule
    \end{tabular}
    \caption{Data Cube Data Sets Overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoints} \\		
      \hline
      ECB & \url{http://ecb.270a.info/sparql} \\
			UIS & \url{http://uis.270a.info/sparql} \\
			IMF & \url{http://imf.270a.info/sparql} \\
			BFS & \url{http://bfs.270a.info/sparql} \\
			FAO & \url{http://fao.270a.info/sparql} \\
			WB & \url{http://worldbank.270a.info/sparql} \\
			FRB & \url{http://frb.270a.info/sparql} \\
			TI & \url{http://transparency.270a.info/sparql} \\
			OECD & \url{http://oecd.270a.info/sparql} \\
			BIS & \url{http://bis.270a.info/sparql} \\
			ABS & \url{http://abs.270a.info/sparql} \\
		\end{tabular}
	\caption{Data Cube Data Sets SPARQL Endpoints}
	\label{tab:data-cube-data-sets-sparql-endpoints}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Data Model Consistency}
           & \rot{ECB}
           & \rot{UIS}
           & \rot{IMF}
           & \rot{BFS}
           & \rot{FAO}
					 & \rot{WB}
					 & \rot{FRB}
					 & \rot{TI}
					 & \rot{OECD}
					 & \rot{BIS}
					 & \rot{ABS}
					 & \rot{IEEE-VIS}
    \\ \midrule
    DATA-MODEL-CONSISTENCY-01 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    DATA-MODEL-CONSISTENCY-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    DATA-MODEL-CONSISTENCY-03 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    DATA-MODEL-CONSISTENCY-04 & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & & & $\checkmark$ \\
		DATA-MODEL-CONSISTENCY-05 &  &  &  &  &  & & & & & & & $\checkmark$ \\
		DATA-MODEL-CONSISTENCY-06 &  &  &  &  &  & \\
		DATA-MODEL-CONSISTENCY-07 &  &  &  &  &  & \\
		DATA-MODEL-CONSISTENCY-08 &  &  &  &  &  & \\
		DATA-MODEL-CONSISTENCY-09 &  &  &  &  &  & \\
		DATA-MODEL-CONSISTENCY-10 &  &  &  &  &  & \\
		DATA-MODEL-CONSISTENCY-11 &  &  &  &  &  & \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Existential Quantifications}
           & \rot{ECB}
           & \rot{UIS}
           & \rot{IMF}
           & \rot{BFS}
           & \rot{FAO}
					 & \rot{WB}
					 & \rot{FRB}
					 & \rot{TI}
					 & \rot{OECD}
					 & \rot{BIS}
					 & \rot{ABS}
					 & \rot{IEEE-VIS}
    \\ \midrule
		EXISTENTIAL-QUANTIFICATIONS-01 & 9 & $\checkmark$ & 11 & 7 & 8 & 77 & 8 & 9 & 7 & 8 & 7 & $\checkmark$ \\
		EXISTENTIAL-QUANTIFICATIONS-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		EXISTENTIAL-QUANTIFICATIONS-03 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 59 & $\checkmark$ & 6 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		EXISTENTIAL-QUANTIFICATIONS-04 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Cardinality Restrictions}
           & \rot{ECB}
           & \rot{UIS}
           & \rot{IMF}
           & \rot{BFS}
           & \rot{FAO}
					 & \rot{WB}
					 & \rot{FRB}
					 & \rot{TI}
					 & \rot{OECD}
					 & \rot{BIS}
					 & \rot{ABS}
					 & \rot{IEEE-VIS}
    \\ \midrule
		MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 &  &  &  &  &  & \\
		EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01 & \ding{55} & 118 & 8 & 8 & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & 12 & \ding{55} & 1,350 \\
		EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Structure}
           & \rot{ECB}
           & \rot{UIS}
           & \rot{IMF}
           & \rot{BFS}
           & \rot{FAO}
					 & \rot{WB}
					 & \rot{FRB}
					 & \rot{TI}
					 & \rot{OECD}
					 & \rot{BIS}
					 & \rot{ABS}
					 & \rot{IEEE-VIS}
    \\ \midrule
		STRUCTURE-01 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		STRUCTURE-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Constraints}
           & \rot{ECB}
           & \rot{UIS}
           & \rot{IMF}
           & \rot{BFS}
           & \rot{FAO}
					 & \rot{WB}
					 & \rot{FRB}
					 & \rot{TI}
					 & \rot{OECD}
					 & \rot{BIS}
					 & \rot{ABS}
					 & \rot{IEEE-VIS}
    \\ \midrule
		PROPERTY-DOMAIN-01 &  &  &  &  &  & \\
		PROPERTY-RANGES-01 &  &  &  &  &  & \\
		DISJOINT-PROPERTIES-01 &  &  &  &  &  & \\
		DISJOINT-CLASSES-01 &  &  &  &  &  & \\
		EQUIVALENT-PROPERTIES-01 &  &  &  &  &  & \\
		UNIVERSAL-QUANTIFICATIONS-01 &  &  &  &  &  & \\
		MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01 &  &  &  &  &  & \\
		CONTEXT-SPECIFIC-VALID-CLASSES-01 &  &  &  &  &  & \\
		CONTEXT-SPECIFIC-VALID-PROPERTIES-01 &  &  &  &  &  & \\
		RECOMMENDED-PROPERTIES-01 &  &  &  &  &  & \\
		VALUE-IS-VALID-FOR-DATATYPE-01 &  &  &  &  &  & \\
		VOCABULARY-01 &  &  &  &  &  & \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets}
    \end{center}
\end{table}

\section{SKOS}

\begin{itemize}
  \item overview over SKOS data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
	\item overview over thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}} (table \ref{tab:thesauri-overview})
\end{itemize}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Thesauri} \\		
      \hline
    TheSoz & Thesaurus for the Social Sciences\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
	  STW & Thesaurus for Economics\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\
	  AGROVOC & AGROVOC Multilingual agricultural thesaurus\tablefootnote{\url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc}} \\
		UNESCO & UNESCO Thesaurus\tablefootnote{\url{http://skos.um.es/sparql/}} \\
		TGN & The Getty Thesaurus of Geographic Names\tablefootnote{\url{http://vocab.getty.edu/sparql}} \\
		EARTh & Environmental Applications Reference Thesaurus\tablefootnote{\url{http://linkeddata.ge.imati.cnr.it/resource/EARTh/}} \\
		ODT & Open Data Thesaurus\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/OpenData}} \\
		SLD & Spanish Linguistic Datasets\tablefootnote{\url{http://linguistic.linkeddata.es}} \\
		SSWT & Social Semantic Web Thesaurus\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/semweb}} \\
		GBA-GU & Thesaurus of the Geological Survey of Austria (GBA) - Geology Unit\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		GBA-GTS & Thesaurus of the Geological Survey of Austria (GBA) - Geologic Time Scale\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		GBA-L & Thesaurus of the Geological Survey of Austria (GBA) - Lithology\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		GBA-LU & Thesaurus of the Geological Survey of Austria (GBA) - Lithotectonic Unit\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		GEMET & GEneral Multilingual Environmental Thesaurus\tablefootnote{\url{http://www.eionet.europa.eu/gemet/}} \\
		EuroVoc & EuroVoc\tablefootnote{\url{http://open-data.europa.eu/de/data/dataset/eurovoc}} \\
		CECCT & Clean Energy and Climate Change Thesaurus\tablefootnote{\url{http://data.reegle.info/thesaurus/guide}} \\
		\end{tabular}
	\caption{Thesauri Abbreviations}
	\label{tab:thesauri-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{6}{c}{\textbf{Counts}}
    \\  \cmidrule{2-7}
    \\       \textbf{Thesauri}
           & \textbf{\rot{triples}}
           & \textbf{\rot{skos:ConceptScheme}}
           & \textbf{\rot{sko:Concept}}
           & \textbf{\rot{skos:broader}}
           & \textbf{\rot{skos:narrower}}
					 & \textbf{\rot{skos:hasTopConcept}}
					 & \textbf{\rot{skos:inScheme}}
    \\ \midrule
    TheSoz & 439,153 & 1 & 8,426 & 13,705 & 13,706 & 0 & 48,529 \\
	  STW & 221,668 & 1 & 13,468 & 13,732 & 13732 & 7 & 13,180 \\
	  AGROVOC & 6,080,477 & 1 & 32,310 & 33,507 & 33,507 & 25 & 32,310 \\
		UNESCO & 288,346 & 9 & 26,714 & 20,028 & 20,028 & 607 & 32,009 \\
		TGN & 16,112,321 & 8 & 2,898,775 & 0 & 0 & 0 & 1,453,767\\
		EARTh & 9,287,364 &  &  &  & \\
		ODT & 3,290 &  &  &  & \\
		SLD & 7,629,211 &  &  &  & \\
		SSWT & 64,698 &  &  &  & \\
		GBA-GU & 25,718 &  &  &  & \\
		GBA-GTS & 7,875 &  &  &  & \\
		GBA-L & 9,317 &  &  &  & \\
		GBA-LU & 9,504 &  &  &  & \\
		GEMET & 372,889,229 &  &  &  & \\
		EuroVoc & 64,477,774 &  &  &  & \\
		CECCT & 191,336 &  &  &  & \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Overview}
		\label{tab:thesauri-overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Thesauri} & \textbf{SPARQL Endpoints} \\		
      \hline
      TheSoz & \url{http://lod.gesis.org/thesoz/sparql} \\
			STW & \url{http://zbw.eu/beta/sparql/stw/query} \\
			AGROVOC & \url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc} \\
			UNESCO & \url{http://skos.um.es/sparql/} \\
			TGN & \url{http://vocab.getty.edu/} \\
			EARTh & \url{http://linkeddata.ge.imati.cnr.it:8890/sparql} \\
			ODT & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/OpenData} \\
			SLD & \url{http://linguistic.linkeddata.es/sparql} \\
			SSWT & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/semweb} \\
			GBA-GU & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicUnit} \\
			GBA-GTS & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicTimeScale} \\
			GBA-L & \url{http://resource.geolba.ac.at/PoolParty/sparql/lithology} \\
			GBA-LU & \url{http://resource.geolba.ac.at/PoolParty/sparql/tectonicunit} \\
			GEMET & \url{http://semantic.eea.europa.eu/sparql} \\
			EuroVoc & \url{http://open-data.europa.eu/de/linked-data} \\
			CECCT & \url{http://poolparty.reegle.info/PoolParty/sparql/glossary}
		\end{tabular}
	\caption{Thesauri SPARQL Endpoints}
	\label{tab:thesauri-sparql-endpoints}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Data Model Consistency}
           & \rot{TheSoz}
           & \rot{STW}
           & \rot{AGROVOC}
					 & \rot{TGN}
           & \rot{UNESCO}
					 & \rot{ODT}
					 & \rot{SSWT}
					 & \rot{GBA-GU}
					 & \rot{GBA-GTS}
					 & \rot{GBA-L}
					 & \rot{GBA-LU}
					 & \rot{CECCT}
    \\ \midrule
    DATA-MODEL-CONSISTENCY-01 &  &  &  &  &  & \\
    DATA-MODEL-CONSISTENCY-02 &  &  &  &  &  & \\
    DATA-MODEL-CONSISTENCY-03 &  &  &  &  &  & \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation}
		\label{tab:thesauri-evaluation-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Labeling and Documentation}
           & \rot{TheSoz}
           & \rot{STW}
           & \rot{AGROVOC}
					 & \rot{TGN}
           & \rot{UNESCO}
					 & \rot{ODT}
					 & \rot{SSWT}
					 & \rot{GBA-GU}
					 & \rot{GBA-GTS}
					 & \rot{GBA-L}
					 & \rot{GBA-LU}
					 & \rot{CECCT}
    \\ \midrule
		LABELING-AND-DOCUMENTATION-01 & 8,426 & 11,508 & 19,829 & $\checkmark$ & & 36 & 1,475 & 6 & 2 & $\checkmark$ & 107 & 486 \\
		LABELING-AND-DOCUMENTATION-02 & $>$1 & \ding{55} & $>$100 & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		LABELING-AND-DOCUMENTATION-03 & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ \\
		LABELING-AND-DOCUMENTATION-04 &  &  &  &  &  & & &  \\
		LABELING-AND-DOCUMENTATION-05 & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 3 \\
		LABELING-AND-DOCUMENTATION-06 & $>$1 & \ding{55} & \ding{55} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation}
		\label{tab:thesauri-evaluation-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Structure}
           & \rot{TheSoz}
           & \rot{STW}
           & \rot{AGROVOC}
					 & \rot{TGN}
           & \rot{UNESCO}
					 & \rot{ODT}
					 & \rot{SSWT}
					 & \rot{GBA-GU}
					 & \rot{GBA-GTS}
					 & \rot{GBA-L}
					 & \rot{GBA-LU}
					 & \rot{CECCT}
    \\ \midrule
		STRUCTURE-01 & 1 & 1,074 & $\checkmark$ & $\checkmark$ &  & 5 & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		STRUCTURE-02 &  &  &  &  &  & \\
		STRUCTURE-03 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		STRUCTURE-04 & 2,906 & $>$1,000 & 726 & $\checkmark$ &  & 12 & 124 & 84 & 256 & $>$54 & 22 & 2,422 \\
		STRUCTURE-05 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & 90 & 5,150 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 9,864 \\
		STRUCTURE-06 & 2 & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 113 \\
		STRUCTURE-07 & 8 & 1,074 & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		STRUCTURE-08 &  &  &  &  &  & \\
		STRUCTURE-09 & 6,741 & $>$3,297 & 135 & $\checkmark$ &  & 2 & 16 & 25 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 81 \\
		STRUCTURE-10 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation}
		\label{tab:thesauri-evaluation-3}
    \end{center}
\end{table}
